EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-04 draft.tex
a minor change
Starting cloud deplyment
@jj please check the starting point of a proposed short subsection on cloud implementation. Please add question remaing and things that are not needed.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Serverless function implementation details. Showing the worker algorithm in each container}
    \label{fig:worker}
\end{figure}

@@

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{worker_new}
    \caption{Serverless function implementation details. Showing the worker algorithm in each container}
    \label{fig:worker}
\end{figure}

@@

\subsection{Deploying to a Cloud Provider}

% This is only an idea of the section
% 
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation.

    A Kubernetes cluster, this provides auto-scaling and management of containerized
    application, but it needs additional configuration for provisioning. All major
    cloud-providers have Kubernetes services.

    A container orchestration service, these services are compatible with docker-compose
    files for configuration and provide transparent provisioning. Examples of these
    services are Amazon Elastic Container Service,  Red Hat Openshift, and Marantis Docker Enterprise.

As a proof-of-concept, we deployed the EvoSwarm application in Amazon Elastic
Container Service (ECS).  Because it needs fewer changes in configuration, 
and it is has a lower cost than a Kubernetes alternative.

We can define an ECS cluster directly on AWS Elastic Cloud VMs or through AWS Fargate.
Fargate is a serverless compute engine for containers that provides automatic provision 
and management of AWS ECS resources. With this service, calculating the cost of execution
is simplified because users only specify the computing units and memory for all the application,
instead of every component.

Using the ECS CLI, we can provision a cluster with a configuration file
specifying the computing resources needed. Multicontainer applications are
deployed to ECS as tasks, and a single cluster can run multiple tasks in
parallel. When using the Fargate service as a backend, tasks are limited to a
maximum of 10 containers.

We deployed an AWS Fargate cluster and defined a Task configuration file with
8GBs of memory and 4096 computing units, equivalent to 4 CPUs. Because of the
ten container limit, we only used seven workers and tested the same function as
in the previous experiment, but save resources only for dimensions 10 and 20.

The results ..
